\section{Application Cases}

This section describes some application cases of the \textit{Micro City}. Some examples can be found in:

\begin{itemize}
    \item \textbf{Shopping Center} - In this context, the guests are the clients and their common objective is to benefit from services buying products sold by commercial activities. The activities are shops and restaurants; they may supply rewards in terms of discounts and cashbacks.
    \item \textbf{City Center} - In this context, the guests are the citizens and they move around a delimited area of the city center in search of events and shops. In this case, the possible rewards might be discounts and cashbacks.
    \item \textbf{Amusement Park} - In this context, the guests are the visitors and they are interested in attractions, restaurants and shows. In this case, the possible rewards may concern discounts and/or accumulable points, exploitable in commercial activities, or the reduction of the waiting time before entering an attraction.
    \item \textbf{Sports Center} - In this context, the guests are the athletes and their objective is to use sports fields and participate in sports tournaments. In this case, the possible rewards may be the reduction of waiting time before using a sports field.
\end{itemize}

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|p{.2\textwidth}|}
        \hline
        \textbf{Micro City} & \textbf{Guests} & \textbf{Activities} & \textbf{Rewards} \\
        \hline
        \case{Shopping Center}{Clients}{Shops}{Discounts/Cashbacks}
        \case{City Center}{Citizens}{Shops \& Events}{Discounts/Cashbacks}
        \case{Amusement Park}{Visitors}{Attractions \& Shows \& Shops}{Discounts/Waiting Time Reduction}
        \case{Fair}{Visitors}{Stands \& Shows}{Accumulable Points/ Waiting Time Reduction}
        \case{Sports Center}{Athletes}{Fields \& Tournaments}{Waiting Time Reduction}
    \end{tabular}
    \caption{Some examples of application cases.}
    \label{tab:examples}
\end{table}